\documentclass{article}

\usepackage{hyperref}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{physics}

\title{Introduction to Quantum Information and Computing - Lecture 6}
\author{Shrikara A, Arnav Negi, Kriti Gupta, Manav Shah, Mohammed Shamil,\\ Shiven Sinha, Swayam Agarwal, Vineeth Bhat, Yash Adivarekar} % add contributors
\date{24th January, 2023}

\begin{document}


    \pagenumbering{gobble}
    \maketitle
    \vfill
    \tableofcontents
    \newpage
    \pagenumbering{arabic}


    %fill
    \section{Quantum Channel}
    \begin{gather*}
     \mathcal{N} _{A \rightarrow B} : \mathcal{B}(\mathcal{H _{A}}) \xrightarrow \mathcal{B}(\mathcal{H _{B}}) 
    \end{gather*}


    where 
        \begin{center}
            \((\mathcal{H _{A}})\) = Hilbert space of input system, 
            
            \( (\mathcal{B}) \) = Set of bounded operators  
        \end{center}
        Quantum channel is trace-preserving since it maps trace-class operators to trace-class operators. 
        
\medskip
        \small
        A matrix with a finite trace represents a trace-class operator. 
        A finite-dimensional matrix is a trace-class operator if it is bounded.
        
\medskip
        \normalsize
        A \textbf{Super Operator} acts on an operator to give an operator.
        
        \subsection{Properties of Quantum Channel}
        For a super operator to be a quantum channel, it has to follow the following properties:
            \begin{enumerate}
                \item Completely positive
                \begin{gather*}
                    id_{B} \otimes \mathcal{N}_{A \rightarrow{} C} (\Phi_{AB}) \geq 0
                \end{gather*}
                where $\Phi _{AB}\geq 0$ and $id$ = identity super operator, and $\phi_{AB}$ is a maximally entangled state.    
                
                \subitem Positivity:
                    $X_{A} \geq 0 \Rightarrow{} \mathcal{N}_{A\rightarrow{} C} (\mathcal{X}_{A}) = \mathcal{Y}_{C} \geq 0$
          
                \item Trace-preserving map
                \begin{gather*}
                    Tr[\rho_{A}] \Rightarrow{} Tr[\mathcal{N}_{A \rightarrow C} (\rho _{A})]
                \end{gather*}
            \end{enumerate}

\section{Joint States}
    \subsection{Product State}
     The density operator of the product state of A and B is the tensor product of the density operators of A and B.
    \begin{gather*}
     \rho _{AB} = \rho _{A} \otimes \sigma _{B}
    \end{gather*}
    In a product state, there is no correlation between the two states. A and B are independent.
    
    \subsection{Separable States}
    The density operator of a separable state is obtained as: 
    \begin{gather*}
            \rho _{AB} =  \sum_{x} p_{x} \rho ^{(x)} _{A} \otimes \sigma ^{(x)} _{B}  \\
    \end{gather*}
    where $p _{x}$ is the probability of each state such that
    \begin{gather*}
            \sum p_{x} = 1,   p_{x} \geq 0
    \end{gather*}
Here, $\rho ^{(x)} _{A} $ and $\sigma ^{(x)} _{B}$ may be pure or mixed states.

    \subsection{Entangled State}
    State which cannot be written as separable states or product of states is in an entangled state.
    \begin{gather*}
        \mathcal{N}_{A \rightarrow C}(\Phi _{AB})
    \end{gather*}
    Dimension, d = $min(dim(\mathcal{H}_{A}), dim(\mathcal{H}_{B}))$\\

    Maximally entangled state: $\Phi_{AB} = \frac{1}{d} \sum_{i,j=0}^{d-1}\ket{i}_{A} \otimes \ket{i}_{B} \bra{j}_{A} \otimes \bra{j}_{B}\\
    =\frac{1}{d} \sum_{i,j=0}^{d-1}\ket{i} \bra{j}_{A} \otimes \ket{i} \bra{j}_{B}
    $

    \section{Kraus Operators: $K_{i}$}
    \begin{gather*}
        \mathcal{N}_{A \rightarrow C} (\cdot) = \sum_{i} K_{i}(\cdot) K_{i}\textsuperscript{\textdagger}
    \end{gather*}
    where
    \begin{gather*}
        \sum K_{i}\textsuperscript{\textdagger} K_{i} =  \mathbb{1}\\
        K_{i} : \mathcal{H}_{A} \rightarrow{} \mathcal{H}_{C}
    \end{gather*}

    For any completely positive, trace-preserving quantum channel, \exists Kraus operators.

    If an \mathcal{N} has Kraus operators $\Rightarrow{}$ it is completely positive and trace-preserving.
\\\\
    Projective measurement is a special case of quantum channel where \mathbb{P}s are Kraus operators.
\end{document}